Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging

### 2016-01-29 writeup/gz_hubble_data.tex

\begin{table*}
\caption{Breakdown of what we can correct out of the GZH data, by sample. \label{hubble_debiasable}}
\begin{tabular}{lrrrrrrr}
\hline\hline
                                   & AEGIS   & COSMOS & GEMS & GOODS-N & GOODS-S & SDSS    & Total \\
\hline
Correctable                        & 2,325   & 20,669 & 2,748 & 1,074  & 1,022   & 0       & 27,838\\
Uncorrectable                      & 1,403   & 19,626 & 1,832 & 271    & 980     & 0       & 24,112\\
No Correction Needed ($z \le 0.3$) & 967     & 11,693 & 1,190 & 280    & 247     & 37,545  & 51,922\\ 
NEI                                & 2,465   & 33,727 & 1,886 & 691    & 2,023   & 0       & 40,792\\
No Redshift Information            & 1,347   & 7,093  & 1,648 & 235    & 641     & 14,316  & 25,280\\
Total                              & 8,507   & 92,808 & 9,304 & 2,551  & 4,913   & 51,861  & 169,944\\
\hline\hline
\end{tabular}
\end{table*}

>>>>

\begin{table*}
\caption{Breakdown of what we can correct out of the Hubble data, by sample. \label{hubble_debiasable}}
\begin{tabular}{lrrrrrrrr}
\hline\hline
                                   & AEGIS   & COSMOS & GEMS & GOODS-N & GOODS-S & GOODS FULL   & SDSS    & Total \\
\hline
Correctable                        & 1,628   & 15,120 & 1,811 & 739    & 502     & 1,850	& 0       & 21,650\\
Uncorrectable                      & 1,869   & 26,184 & 2,407 & 524    & 1,115   & 2,670	& 0       & 34,769\\
No Correction Needed ($z \le 0.3$) & 944     & 11,781 & 1,193 & 258    & 258     & 1,083	& 37,545  & 53,062\\ 
NEI                                & 2,753   & 34,432 & 2,271 & 861    & 2,547   & 4,766	& 0       & 47,630\\
No Redshift Information            & 1,313   & 5,291  & 1,622 & 169    & 491     & 788		& 14,316  & 23,990\\
Total                              & 8,507   & 92,808 & 9,304 & 2,551  & 4,913   & 11,157	& 51,861  & 181,101\\
\hline\hline
\end{tabular}
\end{table*}
